MINOS Handover Plots

### 2024-04-08 minos/validation/handovers.Rmd

out.path <- here::here('output', 'glasgow_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE, drop.zero.weight = TRUE)
```

>>>>

out.path <- here::here('output', 'glasgow_scaled/')
#out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```
